---
title: "Lab_3"
author: "Jessica Jagdeo"
date: "1/23/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

```{r}

library(tidyverse)
library(janitor)
library(here)
library(sf)
library(tmap)

```

## Binary logistic regression: Penguins

Read in the data:
```{r}

gentoo <- read_csv("gentoo_lter.csv")

chinstrap <- read_csv("chinstrap_lter.csv")

penguins <- full_join(chinstrap, gentoo) %>% 
  clean_names() %>% 
  mutate(sex = str_to_lower(sex)) %>% # Changes every string in that column to lowercase
  filter(sex %in% c("male", "female")) # Removes strings that don't match "male" or "female"

```

Now let's graph this:
```{r}

ggplot(penguins, aes(x = sex, y = body_mass_g)) +
  geom_jitter(
    aes(color = sex,
        pch = sex)
  ) +
  facet_wrap(~species)

```

Code Chinstrap penguins as (1) and Gentoo penguins (0):
```{r}

penguin_bin <- penguins %>% 
  mutate(
    sp_binary = case_when(
      species == "Chinstrap penguin (Pygoscelis antarctica)" ~ 1,
      species == "Gentoo penguin (Pygoscelis papua)" ~ 0
    )
  )

```

Run binary logistic regression:
```{r}

penguin_blr <- glm(sp_binary ~ sex + body_mass_g, 
                   family = binomial,
                   data = penguin_bin)

summary(penguin_blr)

# Results:

# An increase in body mass (g) will decrease the probability of the penguin species being Chinstrap. As body mass increases, it is becoming less probable that the penguin in a Chinstrap penguin. 

```

Let's make some predictions for penguins (sort of like classification):

1. What is the probability that the penguin is a Chinstrap penguin if it weighs 4500 grams and is male?
```{r}

df_m4500 <- data.frame(sex = "male", body_mass_g = 4500)

# Find the log odds of this penguin being Chinstrap:
m4500_logodds <- predict(penguin_blr, newdata = df_m4500, type = "link")

# Find the probability
m4500_prob <- predict(penguin_blr, newdata = df_m4500, type = "response")

# If the only types of penguins on this island are Chinstrap and Gentoo and we find recordings of a penguin claiming that it's male and weighs 4500 g, there is a 98% chance that the penguin is Chinstrap. 

```

2. What is the probability that a penguin in Chinstrap if it is recorded as a female of 4000 g?
```{r}

# Create the necessary dataframe for prediction
df_f4000 <- data.frame(sex = "female", body_mass_g = 4000)

# Find the probability
f4000_prob <- predict(penguin_blr, newdata = df_f4000, type = "response")

# If the only types of penguins on this island are Chinstrap and Gentoo and we find recordings of a penguin claiming that it's female and weighs 4000 g, there is a 65% chance that the penguin is Chinstrap. 

```

Let's make an entire dataframe and use it to then make visualize logistic regression outcomes:
```{r}

penguins_mock <- data.frame(
  body_mass_g = rep(seq(3000, 6000, length = 200), 2),
  sex = c(rep("male", 200), rep("female", 200))
)

```

Now let's use those to make predictions for all of them:
```{r}

full_predict <- predict(penguin_blr, newdata = penguins_mock, type = "response", se.fit = TRUE)

# Get those into a dataframe along with the mock data used to create them:

final_df <- data.frame(
  penguins_mock, 
  full_predict$fit,
  full_predict$se.fit
)

colnames(final_df) <- c("penguins_mass", "sex", "probability", "se")
```

Let's graph it:
```{r}

ggplot(final_df, aes(x = penguins_mass, y = probability)) +
  geom_line(aes(color = sex)) +
  geom_ribbon(aes(ymin = probability - se,
                  ymax = probability + se,
                  fill = sex),
              alpha = 0.3)

```

## Now some spatial data with sf

Read in the spatial data using read_sf:
```{r}

cougars <- read_sf(dsn = here("cougar_connections"), layer = "ds1014") %>% 
  clean_names()

```

```{r}

large_corridors <- cougars %>% 
  filter(area_ac > 20000) %>% 
  select(area_ac)

plot(large_corridors)

```

```{r}

cougars_sub <- cougars %>% 
  select(elev_mean)

```

```{r}

ggplot(cougars_sub) +
  geom_sf(aes(fill = elev_mean),
          color = NA)

```

```{r}

tmap_mode("view") # Sets tmap to interactive viewing mode

tm_shape(cougars_sub) +
  tm_fill("elev_mean")

```

